%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Core Member} % Affiliation/role
    {\href{https://gpos.postech.ac.kr}{G-POS (Gamemakers in POSTECH)}} % Organization/group
    {Pohang, S.Korea} % Location
    {May. 2023 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Studied various game genres, acquire related knowledge, and apply it to independently develop games.}
        \item {Have an intensive game development bootcamps during the summer and winter seasons.}
        \item {Conducted seminars on C, C#, and Unity for club freshmen.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {NDM (Nexon Dream Members)} % Organization/group
    {S.Korea} % Location
    {May. 2023 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {NDM is Nexon's university game development club sponsorship program.}
        \item {Participated in NDM Game Development Showcase, Nexon Game Jam.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {UNIDEV} % Organization/group
    {S.Korea} % Location
    {May. 2023 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {UNIDEV is National University Game Development Club Association.}
        \item {Participated in UNICON, UNIJAM.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Core Member \& President at 2025} % Affiliation/role
    {\href{https://plus.or.kr/}{PLUS (Laboratory for UNIX Security in POSTECH)}} % Organization/group
    {Pohang, S.Korea} % Location
    {May. 2024 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Gained expertise in hacking \& security areas, especially interested in Cryptography and Cryptanalysis.}
        \item {Participated on several hacking competition and won a good award.}
        \item {Conducted periodic security checks on overall IT system as a member of POSTECH CERT.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
